### 2014-05-22 lineage-movement.tex

If we also rescale recombination, so that $\rho = r/\sigma^2$,
then 
\begin{align}
    \frac{1}{\sigma^2} \gamma_B(x) \xrightarrow{\sigma \to 0} \rho (1-p(x)) \frac{s_B(x)+s_b(x)}{2} ,
\end{align}
which we can define to be equal to $\rho k(x)$.
In this case, note that since $r = \rho \sigma^2$,
\begin{align}
    M_r(x) \xrightarrow{\sigma \to 0} M(x) = s_B(x) .
\end{align}
Under these assumptions, combining \eqref{eqn:discrete_generator} and \eqref{eqn:deriv_limit},
\begin{align}
    \deriv{t} \E[f(X_{t/\sigma^2}) \given X_0=x ] &\xrightarrow{\sigma \to 0} 
    \frac{1}{2} s_B(x) \dderiv{x} f(x) + \frac{1}{N(x)p(x)} \deriv{x} \left\{ N(x)p(x) s_B(x) \right\}  \deriv{x} f(x) - \rho k(x) f(x) \\
    &= \frac{1}{2} s_B(x) f''(x) + \left( s_B'(x) + \log(N(x)p(x))' s_B(x) \right) f'(x)  - \rho k(x) f(x) ,
\end{align}
i.e.\ $X_{t/\sigma^2}$ converges to a diffusion with drift $\frac{1}{ N(x)p(x)} \deriv{x} ( N(x) p(x) s_B(x) )$ and killed at rate $\rho k(x)$.

@@

@@

@@

    \item Can we make any progress analytically with any of these quantities,
      using the fact that
      \[ \frac{1}{2} p''(x) + s(x) p(x)(1-p(x)) = 0 \quad ?\]

>>>>

If we also rescale recombination, so that $\rho = r/\sigma^2$,
then 
\begin{align}
    \frac{1}{\sigma^2} \gamma_B(x) \xrightarrow{\sigma \to 0} \rho (1-p(x)) \frac{s_B(x)+s_b(x)}{2} ,
\end{align}
which we can define to be equal to $\rho k(x)$.
In this case, note that since $r = \rho \sigma^2$,
\begin{align}
    M_r(x) \xrightarrow{\sigma \to 0} s_B(x) .
\end{align}
Under these assumptions, combining \eqref{eqn:discrete_generator} and \eqref{eqn:deriv_limit},
\begin{align}
    \deriv{t} \E[f(X_{t/\sigma^2}) \given X_0=x ] &\xrightarrow{\sigma \to 0} 
    \frac{1}{2} s_B(x) \dderiv{x} f(x) + \frac{1}{N(x)p(x)} \deriv{x} \left\{ N(x)p(x) s_B(x) \right\}  \deriv{x} f(x) - \rho k(x) f(x) \\
    &= \frac{1}{2} s_B(x) f''(x) + \left( s_B'(x) + \log(N(x)p(x))' s_B(x) \right) f'(x)  - \rho k(x) f(x) ,
\end{align}
i.e.\ $X_{t/\sigma^2}$ converges to a diffusion with drift $\frac{1}{ N(x)p(x)} \deriv{x} ( N(x) p(x) s_B(x) )$ and killed at rate $\rho k(x)$.

@@

\paragraph{Rescaling selection out}
Suppose for the moment that $s_b(x)=1$. 
It hasn't entered here much anyhow.
First note that if we change spatial variables to
\begin{align}
  s(x) = \int_0^x \sqrt{s_B(y)} dy
\end{align}
then $ds = \sqrt{s(x)} dx$, and the generator for the process becomes
\begin{align}
  f \mapsto 
    \frac{1}{2} f''(s) + \log\left( N(s) p(s) s_B(s) \right)' f'(s) - \rho k(s) f(s) .
\end{align}
At first sight this looks like the usual scaling of $\sigma/\sqrt{s}$,
but it isn't, because in the notation I'm using there, $s_B$ is around 1,
i.e.\ $s_B = 1+s$ if $s$ is the usual selection coefficient.

@@

%%%%%%%%%
\section{Integrals against $p$}

Recall that if $N(x)$ is constant, the equilibrium frequency $p(x)$ solves
\[ \frac{1}{2} p''(x) + s(x) p(x)(1-p(x)) = 0 \quad ,\]
where $s(x) = s_B(x)-s_b(x)$,
and that if $s(x) = s$ is constant on a region, the \emph{inverse} solves
\begin{align}
  \frac{dx}{dp} = \frac{1}{\sqrt{sp^2(2p/3-1) + K}},
\end{align}
where $K$ is a constant to make the boundary conditions come out right.

If this is the case, then we can change variables:
\begin{align}
  \int_a^b f(p(x)) dx = \int_{p(a)}^{p(b)} \frac{f(p) dp }{\sqrt{sp^2(2p/3-1) + K}} .
\end{align}
so for instance, 
the denominator for the stationary distribution (dropping the $N$'s)
\begin{align}
  Z &= \int p(y)^2 s_B(y) dy \\
  &= \int \frac{ p (1+s) dp }{ \sqrt{ s (2p/3-1) + K } } .
\end{align}
Note, however, that the first expression makes it clear that if we make the patch bigger, that $Z$ will increase roughly proportionally
-- since this increases the area over which $p(y)\approx 1$.
To make this occur in the integral over $p$ on the second line, 
it must be the case that $K$ is approximately $s/3$ plus a term inversely proportional to the area of the patch.

The integral of $\pi(x) k(x)$ is
\begin{align}
  \frac{1}{Z} \int_a^b p(x)^2(1-p(x))s_B(x)(s_b(x)+s_B(x)) dx = \frac{1}{Z} \int_{p(a)}^{p(b)} \frac{p (1-p) (1+s)(1+s/2) dp }{\sqrt{s(2p/3-1) + K}} .
\end{align}
I have the feeling Barton does similar things in one of his papers,
but haven't been able to track it down.

@@
